\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-11-25 sections/introduction.tex
Update introduction based on PI comments

  Microbiomes are ubiquitous and play an important role in biogeochemical transformations in both natural as well as man-made ecosystems.
  These microbiomes comprise several thousand different microbes interacting with each other and their environment, often through intricate metabolic and signaling relationships.
  The changes in the microbiome can impact the health of the environmental niche in which they reside \cite{HumanMicrobiomeProjectConsortium2012,Lloyd-Price2016} and this can have major implications in health of the human body.
  A mechanistic understanding of the key interactions driving the microbe-microbe and microbe-environment dynamics is necessary in order to analyze the dysbiosis in a healthy microbiome and in the design of modifications to these correct these microbiomes.

  Studies have shown the importance of specific microbial interactions in the healthy human microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
  While direct measurement of interactions is challenging, a lot of effort has gone into measuring correlations.
  Co-occurrence relationships in microbial communities may be driven by microbial interactions, although the extent and nature of their relationship is highly debated.
  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved.
  Bacteria that compete for the same nutrient will have a negative co-occurrence relationship \cite{Ghoul2016} whereas cross-feeding between species leads to a positive co-occurrence relationship \cite{DSouza2018}.
  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.

>>>>

  Microbial communities are ubiquitous and play an important role in biogeochemical transformations in both natural as well as man-made ecosystems.
  These microbiomes comprise several thousand different microbial strains interacting with each other and their environment, often through intricate metabolic and signaling relationships.
  The changes in the microbiome can impact the environmental niche in which they reside \cite{HumanMicrobiomeProjectConsortium2012,Lloyd-Price2016} and for host-associated microbiomes this can have major implications in health of the human body.
  A mechanistic understanding of the key interactions between microbes is necessary in order to analyze the dysbiosis in a healthy microbiome and the design interventions.

  Studies have shown the importance of specific microbial interactions in the healthy microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
  While direct measurement of interactions is challenging, a significant effort has gone into measuring correlations leading to the correlations between microbial abundances being readily available(?)
  Co-occurrence relationships in microbial communities may be driven by microbial interactions, although the extent and nature of their relationship is highly debated.
  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved.
  Bacteria that compete for the same nutrient will have a negative co-occurrence relationship \cite{Ghoul2016} whereas cross-feeding between species leads to a positive co-occurrence relationship \cite{DSouza2018}.
  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.
